### 2014-11-24 paper/6.852 summaries.tex

\documentclass[11pt]{article}
\usepackage{graphicx}    % needed for including graphics e.g. EPS, PS
\topmargin -1.5cm        % read Lamport p.163
\oddsidemargin -0.04cm   % read Lamport p.163
\evensidemargin -0.04cm  % same as oddsidemargin but for left-hand pages
\textwidth 16.59cm
\textheight 21.94cm 
%\pagestyle{empty}       % Uncomment if don't want page numbers
\parskip 7.2pt           % sets spacing between paragraphs
%\renewcommand{\baselinestretch}{1.5} % Uncomment for 1.5 spacing between lines
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{blkarray}
\parindent 0pt		 % sets leading space for paragraphs
\author{Fermi Ma}
\title{6.852 summaries}
\newcommand{\x}{\overline{x}}
\newcommand{\fc}{\frac{x_C}{N}}

\begin{document}
\maketitle

\section{Collaborative Search on the Plane without Communication}

\subsection{Overview}

This paper introduces the \emph{Ants Nearby Treasure Search} problem for modelling collective foraging in animal groups. In the problem, $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location. The time it takes to find treasure is lower bounded by $\Omega(D + D^2/k)$, and this paper shows that this bound can be matched if the agents have knowledge of $k$ up to a constant approximation.

The paper also shows that the agents can potentially perform well without any knowledge of $k$, and it also gives an efficient, uniform algorithm that may be biologically relevant.

\subsection{Formal Problem Statement}

There are $k$ mobile agents searching for treasure in the two-dimensional grid $G$ with vertex set $\mathbb{Z}^2$. All $k$ agents start the search from a central \emph{source} node $s \in G$. An adversary places the treasure at some target node $\tau \in G$ at a \emph{hop distance} $D$ away from $s$. The hop distance is simply the minimum number of grid edges that must be traversed to get from one node to another, and is also known as the taxicab distance. We denote the hop distance from the starting node $s$ to some point $t$ as $d(t)$. The goal of the agents is for one of them to find the treasure by reaching the node $\tau$.

The individual agents are permitted to use any amount of computation and storage necessary. It is assumed that the agents act synchronously, and that they all start their search at the same time $t_0$. Each edge traversal costs one unit of time, so the total time (or cost) it takes to run an algorithm is the number of edges traversed by the first agent to find the treasure. The cost of a given algorithm $\mathcal{A}$ is simply the expected time it takes to find the treasure, which is denoted by $T_\mathcal{A}(D,k)$.

\subsection{An $\Omega(D+D^2/k)$ Lower Bound}

There is a simple $\Omega(D+D^2/k)$ lower bound which follows from the following argument. The time it takes $T$ for an algorithm to run must satisfy $T \geq D$, or else it is not even possible to reach treasure $D$ units away.

Also, $T$ must satisfy $T \geq D^2/4k$. To see why, suppose not. Then $T < D^2/4k$, and in particular $2kT < D^2/2$. Thus, out of all the points that are at most $D$ away from the source $s$, by time $2T$, strictly less than half of them have been visited. This implies that some node at most $D$ units away is visited with probability less than $1/2$ by time $2T$. If the adversary simply places the target at that node, then the expected time to find the treasure is strictly greater than $T$, which is a contradiction.

\subsection{An Asymptotically Optimal Upper Bound Given $k$}

The paper shows that if the agents know the exact value of $k$, an optimal runtime of $O(D+D^2/k)$ can be achieved.

[ALGORITHM DESCRIPTION AND PROOF]

In fact, even if the agents do not know the exact value $k$, and instead only know soem value $k_a$ in the range $k/p \leq k_a \leq kp$, then the running time is only increased by at most $p^2$.

[ADD PROOF]

\subsection{A Uniform Algorithm}

We consider the idea of \emph{uniform algorithms}, which are algorithms for the case where the agents do not know the value of $k$.

\subsection{A Lower Bound for Uniform Algorithms}

\subsection{Harmonic Search}

The harmonic search algorithm is a very simple algorithm that does not perform in iterations. This algorithm is proposed because it is more likely to be used by real ants, as the iterative methods used by the above algorithms may be too complicated.

The algorithm works as follows. 1) The agent chooses a random direction and walks a distance $d$, where the probability of choosing $d$ is roughy inversely proportional to $d$. 2) The agent performs a spiral search for roughly $d^2$ steps. 3) The agent returns to the source.

This algorithm performs well for large values of $k$.

\section{Tradeoffs Between Selection Complexity and Performance when Searching the Plane without Communication}

\subsection{Overview}

\section{Solving the ANTS Problem with Asynchronous Finite State Machines}

\subsection{Overview}

\end{document}

### 2014-11-24 paper/draft.tex

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
\usepackage{subfigure}
%\usepackage{caption} 
%\usepackage{subcaption}
%\usepackage{cite}
\usepackage{hyperref}
\usepackage{url}
\urlstyle{same}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\makeatletter
\let\c@lemma=\c@theorem
\let\c@corollary=\c@theorem
\let\c@fact=\c@theorem
\makeatother

\let\realendproof=\endproof
\def\endproof{\hspace*{\fill}$\Box$\realendproof}

\begin{document}

\mainmatter

\title{Experiments on ANTS Algorithms Without Communication}
\author{Fermi Ma \and Nicolas Rakover \and Erik Waingarten}
\institute{MIT}

\maketitle

\section{Introduction}

\subsection{Related Works}

\section{Algorithms}

We run experiments on three algorithms:
\begin{itemize}
\item FKLS
\item LLNR
\item Harmonic search algorithm
\end{itemize}

Go through thorough theoretical analysis of each. Explain lower bound. Give the model and the motivations.

\subsection{Extending LLNR to uniform}

\section{Experiments and Results}

\subsection{Non-uniform in $n$}

\subsection{Uniform in $n$}

\section{Conclusion}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2014-11-24 code/algorithms/FKLS.py
i think the harmonic search works, need to check distance sampling

@@ -1,3 +1,5 @@
+import math
+import random
 
 class FKLS:
     
@@ -204,4 +206,33 @@ class FKLS2(FKLS):
     def t_max(self):
         return math.floor( math.pow( 2, self.i+2 ) / self.f(self.j) + 0.5 )
 
+class HarmonicSearch(FKLS):
+    
+    def __init__(self, location, delta):
+        FKLS.__init__(self, location, 0,0)
+        self.delta = delta
+        self.normalVariance = 1 / math.sqrt(2) * math.pow((2 + delta), -0.5)
 
+    def chooseNode(self):
+        assert self.step == 'choosing node'
+        self.distance_u = self.sampleDistance()
+        xcoor = random.randint(-self.distance_u, self.distance_u)
+        ycoor = self.distance_u - abs(xcoor)
+        self.u = (xcoor, ycoor)
+        self.step = 'going to node'
+
+    def sampleDistance(self):
+        x = random.random()
+        y = math.floor(1./x)
+        distance_u = math.pow((math.pow(2*y - 1, 2) - 1)/4.0, 1./(2+self.delta))
+        distance_u = int(math.ceil(distance_u))
+        return distance_u
+
+    def returnToSource(self):
+        assert self.step == 'return'
+        self.location = self.source
+        self.step = 'choosing node'
+
+    def t_max(self):
+        return math.pow(self.distance_u, 2 + self.delta)
+    

### 2014-11-24 code/algorithms/test.py

@@ -1,3 +1,4 @@
+import math
 from FKLS import *
 import matplotlib as mpl
 import pylab as pl

### 2014-11-25 code/algorithms/Lines.py
added tests stuff for harmonic and lines

@@ -112,4 +112,12 @@ class LinesUniformInD(LinesNonUniform):
 		else:
 			self.simulation.act()
 
+class LinesUniformInAll(LinesUniformInD):
+        
+        def __init__(self, location, f, K):
+                LinesUniformInD.__init__(self, location, 0, K)
+                self.l = 0
+                self.f = f
 
+        def act(self):
+                return True

### 2014-11-26 code/algorithms/FKLS.py
idk

@@ -223,9 +223,13 @@ class HarmonicSearch(FKLS):
 
     def sampleDistance(self):
         x = random.random()
-        y = math.floor(1./x)
+        print "X", x
+        y = math.ceil(1./x)
+        print "Y", y
         distance_u = math.pow((math.pow(2*y - 1, 2) - 1)/4.0, 1./(2+self.delta))
+        print "D (float)", distance_u
         distance_u = int(math.ceil(distance_u))
+        print "D (int)", distance_u
         return distance_u
 
     def returnToSource(self):

### 2014-12-05 code/simulation/tests.py
testing scenario ready

@@ -5,8 +5,33 @@ from simulation.board import *
 import sys
 import random
 import math
+import pickle
+import datetime
 
 class Tests:
+
+    def runAllTests(self, numAgents, D, trialsPerAgent):
+        types = [{'name':'FKLS1', 'args': None, 'argsName':'no args'},
+                 {'name':'FKLS2', 'args':lambda x: x**2+1, 'argsName': 'function f square'},
+                 {'name':'LinesNonUniform', 'args': 0, 'argsName': 'D'}, # need to overwrite D
+                 {'name':'LinesUniformInD', 'args': 1, 'argsName': 'K = 1'},
+                 {'name':'LinesUniformInAll', 'args': 1, 'argsName': 'K = 1'},
+                 {'name':'HarmonicSearch', 'args': 1, 'argsName': 'delta = 1'}
+                ]
+
+        for anttype in types:
+            print anttype
+            print "Starting Tests..."
+            results = self.testUniform(numAgents, D, trialsPerAgent, anttype)
+            print results
+            print "Pickling..."
+            exp = {'numAgents':numAgents, 'D': D, 'trialsPerAgent':trialsPerAgent}
+            testInfo = {'type': anttype['name'], 'argsDesc': anttype['argsName'], 'data':results,
+                        'experiment': exp }
+            name = 'data/' + anttype['name'] + str(datetime.date.today())
+            outputFile = open(name, 'wr')
+            pickle.dump(testInfo, outputFile)
+            outputFile.close()
 
     def testUniform(self, numAgents, D, trialsPerAgent, type):
         '''
@@ -25,6 +50,8 @@ class Tests:
             distance = D[i]
             experiment = []
             for j in range(trialsPerAgent):
+                if type['name'] == 'LinesNonUniform':            # Super hacky
+                    type['args'] = distance
                 ants = self.generateAnts(k, type)
                 treasureLoc = self.selectTreasureLocation(distance)
                 board = Board(treasureLoc, ants)

### 2014-12-06 code/algorithms/Lines.py
fixed a bug in LinesNonUniform.act(). All Lines algos should run now

@@ -15,22 +15,24 @@ class LinesNonUniform:
 	def act(self):
 		if self.step == 'start':
 			self.start()
-		if self.step == 'up':
+		elif self.step == 'up':
 			self.moveUp()
 		elif self.step == 'down':
 			self.moveDown()
-		if self.step == 'left':
+		elif self.step == 'left':
 			self.moveLeft()
 		elif self.step == 'right':
 			self.moveRight()
-		if self.step == 'origin':
+		elif self.step == 'origin':
 			self.backToOrigin()
 
 	def start(self):
 		if random.random() < 0.5:
 			self.step = 'up'
+			self.act()
 		else:
 			self.step = 'down'
+			self.act()
 
 	def moveUp(self):
 		if random.random() > (1.0/self.D):
@@ -38,8 +40,10 @@ class LinesNonUniform:
 			self.location = (x0 , y0 + 1)
 		elif random.random() < 0.5:
 			self.step = 'left'
+			self.act()
 		else:
 			self.step = 'right'
+			self.act()
 
 	def moveDown(self):
 		if random.random() > (1.0/self.D):
@@ -47,8 +51,10 @@ class LinesNonUniform:
 			self.location = (x0 , y0 - 1)
 		elif random.random() < 0.5:
 			self.step = 'left'
+			self.act()
 		else:
 			self.step = 'right'
+			self.act()
 
 	def moveLeft(self):
 		if random.random() > (1.0/self.D):
@@ -98,7 +104,7 @@ class LinesUniformInD(LinesNonUniform):
 		if self.j == max_j:
 			self.i += 1
 			self.j = 1
-			LinesNonUniform(self.source, 2**self.i)
+			self.simulation = LinesNonUniform(self.source, 2**self.i)
 		else:
 			self.j += 1
 		self.step = 'simulate'
@@ -126,36 +132,39 @@ class LinesUniformInD(LinesNonUniform):
 
 class LinesUniformInAll(LinesUniformInD):
 
-	def __init__(self, location, K):
+	def __init__(self, location, K, f=(lambda x: x**2 + 1)):
 		self.source = location
 		self.K = K
+		self.f = f
 		self.i = 1
-		self.n = 1
+		self.logn = 0
 		self.j = 1
 		self.step = 'simulate'
-		self.simulation = LinesNonUniform(self.source, 2**self.i)
[…]

### 2014-12-06 paper/draft.tex
started writing paper

@@
 \usepackage{url}
+\usepackage{clrscode4e}
 \urlstyle{same}
@@
 
+We study the \emph{Ants Nearby Treasure Search} (ANTS) problem for modelling collective foraging in animal groups.
+$k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location.
+
 \subsection{Related Works}
+
+\section{The Problem Statement}
+
+There are $k$ mobile agents searching for treasure in the two-dimensional grid $G$ with vertex set $\mathbb{Z}^2$.
+All $k$ agents start the search from a central \emph{source} node $s \in G$.
+An adversary places the treasure at some target node $\tau \in G$ at a \emph{hop distance} $D$ away from $s$.
+The hop distance is the minimum number of grid edges that must be traversed to get from one node to another, and is also known as the taxicab distance.
+We denote the hop distance from the starting node $s$ to some point $t$ as $d(t)$.
+The goal of the agents is for one of them to find the treasure by reaching the node $\tau$.
+
+It is assumed that the agents act synchronously, and that they all start their search at the same time $t_0$.
+Each edge traversal costs one unit of time, so the total time (or cost) it takes to run an algorithm is the number of edges traversed by the first agent to find the treasure.
+The cost of a given algorithm $\mathcal{A}$ is the expected time it takes to find the treasure, which is denoted by $T_\mathcal{A}(D,k)$.
+
+\subsection{A Simple Lower Bound}
+
+There is a simple $\Omega(D+D^2/k)$ lower bound which follows from the following argument.
+The time it takes $T$ for an algorithm to run must satisfy $T \geq D$, or else it is not even possible to reach treasure $D$ units away.
+
+Also, $T$ must satisfy $T \geq D^2/4k$.
+To see why, suppose not.
+Then $T < D^2/4k$, and in particular $2kT < D^2/2$.
+Thus, out of all the points that are at most $D$ away from the source $s$, by time $2T$, strictly less than half of them have been visited.
+This implies that some node at most $D$ units away is visited with probability less than $1/2$ by time $2T$.
+If the adversary simply places the target at that node, then the expected time to find the treasure is strictly greater than $T$, which is a contradiction.
+
+Note this lower bound holds even if the agents knows the total number of agents.
 
@@
 
-We run experiments on three algorithms:
+We will focus on three kinds of algorithms:
 \begin{itemize}
-\item FKLS
-\item LLNR
+\item Spiral algorithms
+\item Lines algorithms
 \item Harmonic search algorithm
@@
 
-Go through thorough theoretical analysis of each. Explain lower bound. Give the model and the motivations.
+And each algorithm has two flavours: \emph{uniform} and \emph{non-uniform}.
+We say that an algorithm is non-uniform in parameter $p$ if $p$ is an input to the algorithm.
+If the parameter $p$ is not an input, then the algorithm is uniform in $p$.
+
+For example, a spiral algorithm which is non-uniform in $k$ is the algorithm where agents can know how many total agents there are.
+An algorithm which is non-uniform in $D$ has an upper bound on the hop distance of the treasure.
+
+The spiral and Harmonic search algorithms are similar strategies and were introduced by \cite{feinerman2012collaborative}.
+Both rely on the ``spiral" procedure, in which an agent covers a space of $\sqrt{d}$ grid cells in $O(d)$ time.
+Figure~\ref{fig:spiral} shows a possible spiral routine.
+There will be two kinds of spiral algorithms, non-uniform in $k$ and uniform in $k$.
+There will be three kinds of lines algorithms, non-uniform in $D$, non-uniform in $k$, and uniform in both $k$ and $D$.
+The Harmonic search algorithm is extremely simple and uniform in both $k$ and $D$.
+
+\begin{figure}
+\centering
+\label{fig:spiral}
+\includegraphics[width=0.4\linewidth]{justspiral.pdf}
+\caption{Possible spiral, covering $\sqrt{d}$ grid cells in $O(d)$ time}
+\end{figure}
+
+\subsection{Spiral Algorithms}
+
+The following short explanations are from \cite{feinerman2012collaborative}.
+
+\subsubsection{Non-uniform in $k$}
+
+Given the number of agents taking part in the search, we could imagine an algorithm in which the grid in divided into $k$ parts, similar to a pizza being divided into $k$ equal parts.
+Each agent could cover his portion, and this would yield an asymptotically optimal algorithm.
+However, this assumes that the agents can communicate with each other and decide which portion belongs to which agent.
+
+In order to get around this, we can introduce some randomization.
+If each agent picks a random grid cell within some distance $D$, travels to that distance and performs a spiral of sufficiently large size, it can expect that all agents together will search new areas.
+If we repeat this sufficiently many times, we can expect that the whole area within distance $D$ was covered.
+Then we just need to estimate the value of $D$.
+
+This is what the spiral algorithms does when its non-uniform in $k$.
+
+\begin{codebox}
+\Procname{Each agent performs the following double loop}
+\li \For $j$ from $1$ to $\infty$, \Then
+\li \For $i$ from $1$ to $j$ \Then
+\li Go to a node chosen uniformly at random from nodes a distance $2^{i}$
+\li Perform a spiral search for $2^{2i+2}/k$ steps
+\li Return to source \End \End 
+\end{codebox}
+
+We provide a sketch of the proof to show the algorithm has expected running time $O(D + D^2/k)$.
+Note that the time until agents reach some value of $j$ is $O(2^j + 2^{2j}/k)$.
+Also, note that once $i \geq \log D$, the spiral will intersect the ball of radius $D$ significantly, and so the probability that an agent finds the treasure is some constant $\beta$.
+Therefore, the probability that no agents find it after $l$ phases of $i$ is $(1 - \beta/k)^{kl}$, which is also at most some constant probability $\gamma$.
+
+So for each additional $l$ values of $j$ once $j = \lceil \log D \rceil$, there are $l^2/2$ phases where $i \geq \log D$, and so the probability that a round takes $O(2^{j + l} + 2^{2(j+l)}/k)$ is $\gamma^{l^2/2}$, and so in the computation of the expected value, the sum of all $l$ converges to some constant.
+And we are left with a runtim of $O(2^{j} + 2^{2j}/k)$ for $j = \log D$.
+This finishes the sketch.
+
+\subsubsection{Uniform in $k$}
+
+Once we have the spiral algorithm non-uniform in $k$, we can make it uniform in $k$ by successively doubling estimates of $k$.
+This means that at each stage, we take a guess of what $k$ is, and we simulate the algorithm.
+There is some additional bookkeeping to ensure that enough iterations are made, but the optimization is similar.
+There is higher lower bound on how fast these algorithms can run, and we get a multiplicative factor of $f(\log k)$, where $f$ is a function such that $\sum \dfrac{1}{f(n)}$ converges.
+There is a corresponding lower bound that shows this algorithm is asymptotically optimal.
+
+\subsection{Lines Algorithm}
+
+The lines algorithm is the study of \cite{lenzen2014trade}, where they cover a lines algorithm which is non-uniform in $D$ and non-uniform in $k$.
+We use the ideas of \cite{feinerman2012collaborative} to design a lines algorithm which is uniform in both $k$ and $D$.
 

### 2014-12-06 code/simulation/tests.py

@@ -11,10 +11,10 @@ import datetime
 class Tests:
 
     def runAllTests(self, numAgents, D, trialsPerAgent):
-        types = [{'name':'FKLS1', 'args': None, 'argsName':'no args'},
-                 {'name':'FKLS2', 'args':lambda x: x**2+1, 'argsName': 'function f square'},
-                 {'name':'LinesNonUniform', 'args': 0, 'argsName': 'D'}, # need to overwrite D
-                 {'name':'LinesUniformInD', 'args': 1, 'argsName': 'K = 1'},
+        types = [#{'name':'FKLS1', 'args': None, 'argsName':'no args'},
+                 #{'name':'FKLS2', 'args':lambda x: x**2+1, 'argsName': 'function f square'},
+                 #{'name':'LinesNonUniform', 'args': 0, 'argsName': 'D'}, # need to overwrite D
+                #{'name':'LinesUniformInD', 'args': 1, 'argsName': 'K = 1'},
                  {'name':'LinesUniformInAll', 'args': 1, 'argsName': 'K = 1'},
                  {'name':'HarmonicSearch', 'args': 1, 'argsName': 'delta = 1'}
                 ]

### 2014-12-08 paper/draft.tex
starting final draft and some data

@@
 We use the ideas of \cite{feinerman2012collaborative} to design a lines algorithm which is uniform in both $k$ and $D$.
+The lines algorithm has many optimizations since \cite{lenzen2014trade} are trying to reduce \emph{selection complexity}.
+Selection complexity is a metric which measures how likely an algorithm is to occur naturally in nature.
+Of course, this notion is very vague, but formally, the selection complexity $\chi$ of an algorithm $A$ is $\chi(A) = b + \log l$ where $b$ is the amount of memory usage and $l$ is smallest $l$ for which the algorithm does not need finer probabilities than $2^{-l}$.
+In \cite{lenzen2014trade}, Lenzen et al.
+provided a lines algorithm with selection complexity $O(\log \log D)$.
+
+\subsubsection{Non-uniform in $D$} First, we will explain the simple lines algorithm which is non-uniform in $D$.
+Remember, $D$ is an upper bound on the distance the treasure.
+The lines algorithm is very simple to explain.
+With probability $\frac{1}{2}$, an agent moves up, otherwise, it moves down.
+Then it continues moving in that direction until a coin with head probability $\frac{D-1}{D}$ lands on tails.
+It repeats the process for the left and right directions.
+The pseudocode is shown, $C_p$ will denote a coin which lands heads with probability $p$, and so $C_p$ will return a 0 or 1, with 0 denoting heads.
+
+The algorithm relies on it novel way of walking in lines by approximately counting. The following procedure shows how an agent would move in a particular direction.
+
+\begin{codebox}
+\Procname{moveDirection(dir)}
+\li \While $C_{\frac{D-1}{D}} = 0$ \Then
+\li agent moves in direction dir \End
+\end{codebox}
+
+Note that the above algorithm, while it uses contant memory, it does need to sample from a distribution with probability as fine as $\frac{1}{D}$. This is fine, since in this case, $l = \log D$. 
+Now that we know how agents move in a particular direction, they randomly pick a direction to travel.
+
+\begin{codebox}
+\Procname{Each agent performs the following iteration}
+\li dir[0] $\leftarrow$ up, dir[1] $\leftarrow$ down
+\li $i \leftarrow C_{\frac{1}{2}}$
+\li moveDirection($i$)
+\li \If $C_{\frac{1}{2}} = 0$ \Then
+\li moveDirection(left)
+\li \Else moveDirection(right) \End \End
+\li return to origin
+\end{codebox}
+
+The one thing to note is that the last line, ``return to origin" would need to keep the location of the ant.
+This would require $\log D$ memory, which we cannot afford; however, it is an assumption in the model that agents can return to the origin.
+
+% TO DO
+The sketch of the proof of correctness is the following ...????
+
+\subsubsection{Uniform in $D$}
 

### 2014-12-09 code/simulation/tests.py
changed values of K

@@ -11,11 +11,11 @@ import datetime
 class Tests:
 
     def runAllTests(self, numAgents, D, trialsPerAgent):
-        types = [#{'name':'FKLS1', 'args': None, 'argsName':'no args'},
-                 #{'name':'FKLS2', 'args':lambda x: x**2+1, 'argsName': 'function f square'},
-                 #{'name':'LinesNonUniform', 'args': 0, 'argsName': 'D'}, # need to overwrite D
-                #{'name':'LinesUniformInD', 'args': 1, 'argsName': 'K = 1'},
-                 {'name':'LinesUniformInAll', 'args': 1, 'argsName': 'K = 1'},
+        types = [{'name':'FKLS1', 'args': None, 'argsName':'no args'},
+                 {'name':'FKLS2', 'args':lambda x: x**2+1, 'argsName': 'function f square'},
+                 {'name':'LinesNonUniform', 'args': 0, 'argsName': 'D'}, # need to overwrite D
+                 {'name':'LinesUniformInD', 'args': 6, 'argsName': 'K = 6'},
+                 {'name':'LinesUniformInAll', 'args': 6, 'argsName': 'K = 6'},
                  {'name':'HarmonicSearch', 'args': 1, 'argsName': 'delta = 1'}
                 ]
 

### 2014-12-09 paper/draft.tex
added stuff to intro

@@
 $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location.
+The problem is a generalization of a previously studied problem, the \emph{cow-path} problem, which is the case where $k = 1$.
 
-\subsection{Related Works}
+Our project is a combination of a reading project and an experimental project.
+For the reading project component, we survey three algorithms, two of which are by Feinerman et al., and the other by by Lenzen et al.
+The two algorithms by Feinerman et al.
+are the \emph{spiral} algorithm and the \emph{harmonic} algorithm.
+We name the algorithm by Lenzen et al.
+the \emph{lines} algorithm.
+For these algorithms, we consider case of uniformity, where all agents know the value of either $D$ or $k$, and the case of non-uniformity, where a value is unknown.
 

### 2014-12-09 paper/draft.tex
added more stuff to intro. intro should be done

--- 2014-12-08 paper/draft.tex
@@
 $k$ identical probabilistic agents search for treasure located by an adversary $D$ units away from a central location.
+The problem is a generalization of a previously studied problem, the \emph{cow-path} problem, which is the case where $k = 1$.
 
-\subsection{Related Works}
+Our project is a combination of a reading project and an experimental project.
+For the reading project component, we survey three known algorithms for the ANTS algorithm by Feinerman et al.
+and Lenzen et al.
+For the experimental project, we show the results of tests run on these algorithms to determine the constants in their runtimes.
 
-\section{The Problem Statement}
+The paper is organized as follows.
+In Section~\ref{problem statement}, we formally state and motivate the problem.
+We also give a simple argument for why any algorithm solving the problem takes $\Omega(D+D^2/k)$ time.
+We then outline different algorithm types, and give high-level overviews of the spiral, harmonic, and lines algorithms.
+In Section~\ref{spiral}, we give a more in-depth explanation of the details of the spiral algorithm of Feinerman et al.
+We do this for the harmonic algorithm in Section~\ref{harmonic}, and for the lines algorithm in Section~\ref{lines}.
+In Section~\ref{experiments}, we shift our focus to the experimental part of our project.
+In that section, we describe our hypotheses, our experimental setup, the results, and our interpretation of the results.
+We give concluding remarks in Section~\ref{conclusion}.
+
+\section{Problem Setup and Basics}
+\label{problem statment}
 
@@
 Note this lower bound holds even if the agents knows the total number of agents.
-
-\section{Algorithms}
 
@@
 
-\subsection{Spiral Algorithms}
+\section{Spiral Algorithms}
+\label{spiral}
 
@@
 
-\subsection{Lines Algorithm}
+\section{Harmonic Algorithm}
+\label{harmonic}
+
+\section{Lines Algorithm}
+\label{lines}
 
@@
 \section{Experiments and Results}
+\label{experiments}
 
@@
 \section{Conclusion}
+\label{conclusion}
 

### 2014-12-09 paper/draft.tex
added harmonic search section

@@
 \section{Problem Setup and Basics}
-\label{problem statment}
+\label{problem statement}
 
@@
 
+\subsection{Types of Algorithms}
 We will focus on three kinds of algorithms:
@@
 
+The following is a brief explanation of the Harmonic search algorithm, which, as mentioned earlier, is uniform in both $k$ and $D$.
+
+The main idea is to avoid maintaining a state associated with an estimate of $D$ by randomly regions in the plane such that smaller $D$ will be explored earlier more often.
+More specifically, the procedure as presented in \cite{feinerman2012collaborative} is composed of the following three steps, performed indefinitely: (1) choose a random direction and walk a distance $d$ in that direction from the source, where $d$ is sampled with probability approximately inversely proportional to $d$, (2) do a spiral search for time $\sim d^2$, and (3) return to the source.
+
+The expected performance of the algorithm is determined by a fixed value $\delta > 0$.
+The formal description of the algorithm, shown below, uses the probability distribution $p(u) := \frac{c}{d(u)^{2+\delta}}$, where $u$ is a point in the plane, $d(u)$ the distance from the source to $u$, and $c$ a normalizing factor.
+The following is performed by each agent:
+
+\begin{codebox}
+\li \textbf{begin}
+\Then 
+\li Go to node $u$ with probability $p(u)$
+\li Perform spiral search for time $t(u) := d(u)^{2+\delta}$
+\li Return to source 
+\End
+\li \textbf{end} 
+\end{codebox}
+
+The performance guarantees of the algorithm are stated formally below. For a proof of the statement, please refer to \cite{feinerman2012collaborative}: \\
+
+\emph{
+Let $\delta \in (0,0.8]$.
+For every $\epsilon > 0$, there exists a positive real number $\alpha$ such that if the number $k$ of agents is greater than $\alpha D^{\delta}$, then with probability at least $1-\epsilon$, the expected running time of the harmonic algorithm is $O( D + \frac{D^{2+\delta}}{k})$.
+}
+
 \section{Lines Algorithm}
@@
 
-\subsection{Extending LLNR to uniform}
-
 \section{Experiments and Results}
@@
 
-\subsection{Non-uniform in $n$}
+\subsection{Hypotheses}
 
-\subsection{Uniform in $n$}
+\subsection{Experimental Setup}
+
+\subsection{Findings}
+
+\subsection{Interpretation}
 

### 2014-12-09 paper/draft.tex
starting experiments

@@
 
-\subsection{Hypotheses}
+In this section, we show our results for the experiments we ran on the algorithms mentioned above.
+We do not go into detail regarding the various implementations of the algorithms, but all of the code, along with the data used is available online hosted in the git repository: \url{https://github.com/erikwaing/6.852-Ants.git}.
 
-\subsection{Experimental Setup}
+We implemented the three algorithms, in the possible different uniformity flavours.
+Even though \cite{lenzen2014trade} does not go into detail on how to make the Lines algorithm uniform in $k$, we apply the same techniques as in \cite{feinerman2012collaborative}.
+This allows us to compare the algorithms on an equal setting, with both non-uniform in $k$ and uniform in $k$ flavours.
+
+In the Lines algorithm, there are optimizations made in order to keep memory low.
+For example, in the outer loop of the Lines algorithm which is uniform in $D$, but not in $n$, there is some approximate counting.
+We note that the algorithm still works with the same runtime if instead of the approximate couting, we looped for as long as the expected value of the number of loops.
+This keeps the expected runtime the same, and decreases the variance runtime, which will allow us to converge to constants experimentally quicker.
+These approximate countings were made in order to optimize memory, and we are only focused on the runtime of the algorithms.
+
+\subsubsection{Experimental Setup}
+
+We had to run the Spiral algorithm and the Lines algorithm differently from the Harmonic Search algorithm.
+This is because the Harmonic Search requires arbritrary fine probabilites.
+The technique we used for implementing the Harmonic Search relies on sampling uniformly from the interval $(0, 1)$, and then applying some transformations.
+Since we implemented the algorithm in python, and used \texttt{random.random()} in order to sample uniformly from $(0,1)$, we are limited by the granurality of the python module.
+This means that our current implementation of the Harmonic Search has an upper bound on how far $D$ can be.
+We believe finding better ways to implement this algorithm is an interesting research direction, both in the theoretical algorithms world, as well as the experimental algorithms world.
+
+For testing the Lines and Spiral algorithms, we ran the following series of experiments. 
+\begin{enumerate}
+\item We set $D = 40$, and left it at 40 for the whole experiments. 
+\item We vary $k$ from $10$ to $200$ inclusive in intervals of 10. 
+\item We run each algorithm with each value of $k$ for 100 iterations.
+\item We run the experiments on a random placement of the treasure within hop distance $D$ from the origin, which is our source.
+\end{enumerate}
+
+For the Harmonic Search algorithm, we were only able to test it for $D = 10$, since for higher values of $D$, the algorithm became prohibitively expensive.
+We varied $k$ from 10 to 200 inclusive in intervals of 10 as with Lines and Spiral, and we tested each for 100 times, with randomly placed treasures.
+
+\subsubsection{Hypothesis} We hypothesized that the Lines algorithm will be worse, it terms of runtime, compared to the Spiral algorithm.
+This stems from the fact that the Lines algorithm is optimizing for selection complexity, which would lead to an algorithm that relies on more randomization and iteration.
+In fact, in the proof of correctness of the Lines algorithm, many times, the proofs use the asymptotics to engulf some smaller order terms.
 
 \subsection{Findings}
+
+After running the experiments on all five algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$,
 

### 2014-12-09 paper/draft.tex
adding images and graphs

@@
 %\usepackage{amsthm}
-\usepackage{subfigure}
+\usepackage[tight,footnotesize]{subfigure}
 %\usepackage{caption} 
@@
 We varied $k$ from 10 to 200 inclusive in intervals of 10 as with Lines and Spiral, and we tested each for 100 times, with randomly placed treasures.
+For the Harmonic Search algorithm we let $\delta = 1$.
+For the Lines algorithm, we let $K = 6$.
+
+When done with all the iterations, we compute the average time per 100 experiments and assume that this is the expected value.
 
@@
 
-After running the experiments on all five algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$,
+After running the experiments on all six algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$, Lines non-uniform in $D$, Lines uniform in $D$, but not in $n$, Lines uniform in $n$ and $D$, and Harmonic Seach).
 
-\subsection{Interpretation}
+\subsubsection{Non-uniform in $k$} For non-uniform in $k$ algorithms, we assume that the expected runtime of the algorithms is given by the following formula
+\[ E[T] = c_1 + c_2 / k \]
+Where we are keeping $D = 40$.
+So we are looking to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm.
+Figure~\ref{nonuniformresultsone} and Figure~\ref{nonuniformresultstwo} shows the $k$ being graphed against $k * E[T]$, which we expect to be linear with solve $c_1$ and intercept $c_2$.
+Using linear regression, we are able to estimate the values of $c_1$ and $c_2$.
+\begin{center}
+\begin{tabular}{l | c c}
+\text{Algorithm} & $c_1$ & $c_2$ \\
+\hline
+\text{Spiral} 	   &147 & 21567 \\
+\text{Lines}	   & 896 & 32730 
+\end{tabular}
+\end{center}
+
+\begin{figure}
+\centering
+\label{nonuniformresultsone}
+\includegraphics[width=0.5\linewidth]{FKLS1.png}
+\caption{Spiral algorithm non-uniform in $k$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\begin{figure}
+\centering
+\label{nonuniformresultstwo}
+\includegraphics[width=0.5\linewidth]{LinesUniformInD.png}
+\caption{Lines algorithm non-uniform in $k$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\subsubsection{Uniform in $k$} For uniform in $k$ algorithms, we assume that the expected runtime of the algorithms is given by the following formula
+\[ E[T] = f(\log k)(c_1 + c_2 / k) \]
+Where we set $f(x) = x^2 + 1$. This satisfies all our constraints from the theorems in the paper.
+Again, we keep $D = 40$ and we want to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm.
+Figure~\ref{uniformresultsone} and Figure~\ref{uniformresultstwo} shows the $k$ being graphed against $k * E[T]/f(\log k)$, which we expect to be linear with solve $c_1$ and intercept $c_2$.
+Using linear regression, we are able to estimate the values of $c_1$ and $c_2$.
+\begin{center}
+\begin{tabular}{l | c c}
+\text{Algorithm} & $c_1$ & $c_2$ \\
+\hline
+\text{Spiral} 	   &222 & 19954 \\
+\text{Lines}	   & 284 & 76762 
+\end{tabular}
+\end{center}
+
+\begin{figure}
+\centering
+\label{uniformresultsone}
+\includegraphics[width=0.5\linewidth]{FKLS2.png}
+\caption{Spiral algorithm uniform in $k$, $kE[T]/f(\log k)$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\begin{figure}
+\centering
+\label{uniformresultstwo}
+\includegraphics[width=0.5\linewidth]{LinesUniformInAll.png}
+\caption{Lines algorithm non-uniform in $k$, $kE[T]/f(\log k)$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\subsubsection{Interpretation}
+This shows that in fact, when only analyzing runtime.
+The Spiral algorithm performs better than the Lines algorithm in both uniform and non-uniform cases.
+This of course, was expected, since the Lines algorithm optimizes for memory.
+
+Some interesting thing we noted is that when running the Lines algorithm in the non-uniform flavour in $D$, we noted that there were lower order terms which were important in the runtime.
+Figure~\ref{nonuniforminD} and Figure~\ref{nonuniforminDtwo} show how there are lower order terms that are hidden in the asymptotics that do make a difference in the experiments for small $k$.
+In fact, the assumption that $E[T] = c_1 + c_2 / k$ gives us the graph Figure~\ref{nonuniforminD} being a line, whereas the assumption $E[t] = c_1/ k + c_2 / k^2$ gives us the graph Figure~\ref{nonuniforminDtwo} being a line, which is much more accurate.
+
+\begin{figure}
+\centering
+\label{nonuniforminD}
+\includegraphics[width=0.5\linewidth]{LinesNonUniformnT.png}
+\caption{Lines algorithm non-uniform in $D$, $kE[T]$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\begin{figure}
+\centering
+\label{nonuniforminDtwo}
+\includegraphics[width=0.5\linewidth]{LinesNonUniformn2T.png}
+\caption{Lines algorithm non-uniform in $D$, $k^2E[T]$ is the $y$-axis and $k$ is in the $x$-axis}
+\end{figure}
+
+\subsection{Harmonic Search}
+
+We assume that the expected value for the runtime of the Harmonic Search algorithm is given by the following formula
+\[ E[T] = c_1 + c_2 / k \]
+and we compute the constants $c_1$ and $c_2$. We get that for $D=10$, $c_1 = 148$ and $c_2 = 2319$. Figure~\ref{harmonic}
+
+\begin{figure}
+\centering
+\label{harmonic}
+\includegraphics[width=0.5\linewidth]{Harmonic.png}
+\caption{Harmonic Search algorithm, $kE[T]$ is the $y$-axis and $k$ is the $x$-axis.}
+\end{figure}
 

### 2014-12-09 paper/draft.tex
added a conclusion

@@
 
+In this paper, we have surveyed the recent literature on the Ants Nearest Treasure Search problem, and have identified three prominent algorithms: the spiral algorithm, the harmonic algorithm, and the lines algorithm.
+For each algorithm, we considered cases where they are either uniform or not uniform in the variables $D$ and $k$.
+The lines algorithm was motivated by the idea of a selection complexity, a parameter that roughly models how complex a certain algorithm is.
+While the spiral and harmonic algorithms achieved good / optimal asymptotic bounds, the lines algorithm could do so while maintaining a low (favorable) selection complexity.
+
+Due to the relative simplicity of the lines algorithm, we conjectured that the good asymptotic runtime of the lines algorithm was hiding its costs in constant factors.
+We ran experiments comparing the three algorithms with each other, which confirmed our intuition that the lines algorithm had the worst actual runtimes.
+In fact, it turned out that the lines algorithm had a large $O(1/k^2)$ term that did not show up in the asymptotics, but mattered for the values of $k \leq 200$ that we tested.
+We claim that these $k$ are worth considering, as many real ant colonies such as those made by acorn ants can have $k$ values of that size.
+
+Our work leaves some questions unresolved, and given more time, we would have liked to pursue some of these lines of inquiry.
+One question that we would like to know is what the exact values of constants are as we vary the parameter $D$.
+Another issue we had was that when we performed simulations of the harmonic search algorithm, we did not have a good way of sampling from the theoretical probability distribution.
+Improving this sampling technique would increase the accuracy of our results.
+Finally, we would like to consider the problem of placing treasure in an adversarial sense.
+Note that when we randomly place treasure, as we did in simulations, the question is how long it takes for us to find this random treasure in expectation.
+When we adversarially place treasure at distance $D$, it is assumed that the treasure is the last distance $D$ square the ants reach, so the problem is simply to fully cover an area of space.
+We wonder how considering adversarial placement of treasure would impact our results.
+
 \bibliographystyle{plain}

### 2014-12-09 paper/draft.tex
added stuff for Lines uniform in k

--- 2014-12-09 paper/draft.tex
@@
 
-\section{Lines Algorithm}
+\section{Lines Algorithms}
 \label{lines}
@@
 \subsubsection{Uniform in $D$}
+
+\subsection{Uniform in $k$}
+
+Since we ultimately want to compare the algorithms discussed via simulations, we felt it was necessary to extend the lines algorithms with a variant uniform in $k$, which we could then compare with the uniform spiral algorithm and harmonic search.
+
+The main idea for achieving uniformity in $k$ is borrowed from \cite{feinerman2012collaborative}: we start with a small guess for $k$, run the algorithm uniform in $D$ under this assumption, and then double out guess for $k$ and repeat.
+The implementation actually interleaves the increments of the $D$ and $k$ estimates, running one iteration of the non-uniform subroutine for each estimate.
 

### 2014-12-09 paper/draft.tex
added Lines uniform in D

@@
 
-\subsection{Uniform in $k$}
+The main idea behind the variant uniform in $D$ is that each agent maintains a guess for $D$, which it increases over time, and for each estimate is runs a certain number of iterations of the non-uniform routine (with the current estimate of $D$).
+
+Specifically, the algorithm consists of two loops: an outer, deterministic loop that doubles the guess of $D$ at each iteration (starting with the guess $D = 2$), and an inner loop that flips a coin at each iteration and stops when the coin lands tails.
+The coin flipped has probability of tails given by $\frac{1}{2^p}$, where roughly $p := K + \max \{ \log D - \lfloor \log k \rfloor, 0 \}$.
+Each time the coin lands heads, we run an iteration of the non-uniform algorithm.
+
+This algorithm matches, in expectation, the lower bound of $O(D + \frac{D^2}{k})$.
+
+\subsubsection{Uniform in $k$}
 
@@
 The main idea for achieving uniformity in $k$ is borrowed from \cite{feinerman2012collaborative}: we start with a small guess for $k$, run the algorithm uniform in $D$ under this assumption, and then double out guess for $k$ and repeat.
-The implementation actually interleaves the increments of the $D$ and $k$ estimates, running one iteration of the non-uniform subroutine for each estimate.
+The implementation actually interleaves the increments of the $D$ and $k$ estimates, running a certain number of iterations of the non-uniform subroutine for each estimate.
 

### 2014-12-09 paper/draft.tex
modified experiments section

@@
 
-We implemented the three algorithms, in the possible different uniformity flavours.
-Even though \cite{lenzen2014trade} does not go into detail on how to make the Lines algorithm uniform in $k$, we apply the same techniques as in \cite{feinerman2012collaborative}.
-This allows us to compare the algorithms on an equal setting, with both non-uniform in $k$ and uniform in $k$ flavours.
+We implemented the three algorithms, in the possible different uniformity flavors.
+Even though \cite{lenzen2014trade} does not go into detail on how to make the Lines algorithm uniform in $k$, we apply the same techniques as in \cite{feinerman2012collaborative} to do so.
+This allows us to compare the algorithms on an equal footing, with both non-uniform in $k$ and uniform in $k$ variants.
 
@@
 We note that the algorithm still works with the same runtime if instead of the approximate couting, we looped for as long as the expected value of the number of loops.
-This keeps the expected runtime the same, and decreases the variance runtime, which will allow us to converge to constants experimentally quicker.
-These approximate countings were made in order to optimize memory, and we are only focused on the runtime of the algorithms.
+This keeps the expected runtime the same, and decreases the variance of the runtime, which will allow us to converge to constants experimentally quicker.
+These approximate countings were made in order to optimize memory, as we are only focused on the runtime of the algorithms.
 
@@
 Since we implemented the algorithm in python, and used \texttt{random.random()} in order to sample uniformly from $(0,1)$, we are limited by the granurality of the python module.
-This means that our current implementation of the Harmonic Search has an upper bound on how far $D$ can be.
-We believe finding better ways to implement this algorithm is an interesting research direction, both in the theoretical algorithms world, as well as the experimental algorithms world.
+This means that our current implementation of the Harmonic Search has an upper bound on how large $D$ can be.
+We believe that finding better ways to implement this algorithm is an interesting research direction.
 
@@
 \begin{enumerate}
-\item We set $D = 40$, and left it at 40 for the whole experiments. 
-\item We vary $k$ from $10$ to $200$ inclusive in intervals of 10. 
+\item We set $D = 40$, and left it at 40 for the whole experiment. 
+\item We vary $k$ from $10$ to $200$ inclusive in step sizes of 10. 
 \item We run each algorithm with each value of $k$ for 100 iterations.
@@
 For the Harmonic Search algorithm, we were only able to test it for $D = 10$, since for higher values of $D$, the algorithm became prohibitively expensive.
-We varied $k$ from 10 to 200 inclusive in intervals of 10 as with Lines and Spiral, and we tested each for 100 times, with randomly placed treasures.
+We varied $k$ from 10 to 200 inclusive in steps of 10 as with Lines and Spiral, and we tested each 100 time with randomly placed treasures.
 For the Harmonic Search algorithm we let $\delta = 1$.
-For the Lines algorithm, we let $K = 6$.
+For the Lines algorithm, we let $k = 6$.
 
-When done with all the iterations, we compute the average time per 100 experiments and assume that this is the expected value.
+When done with all the iterations, we computed the average time for the 100 experiments and treat this is as the expected value.
 
-\subsubsection{Hypothesis} We hypothesized that the Lines algorithm will be worse, it terms of runtime, compared to the Spiral algorithm.
-This stems from the fact that the Lines algorithm is optimizing for selection complexity, which would lead to an algorithm that relies on more randomization and iteration.
+\subsection{Hypotheses}
+
+We hypothesized that the Lines algorithm will be worse in terms of runtime when compared to the Spiral algorithm.
+This stems from the fact that the Lines algorithm is optimizing for selection complexity, which would lead to an algorithm that relies on more randomization and iterations.
 In fact, in the proof of correctness of the Lines algorithm, many times, the proofs use the asymptotics to engulf some smaller order terms.
+We expect that these smaller order terms will show up in the testing.
 
@@
 
-After running the experiments on all six algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$, Lines non-uniform in $D$, Lines uniform in $D$, but not in $n$, Lines uniform in $n$ and $D$, and Harmonic Seach).
+After running the experiments on all six algorithms (Spiral non-uniform in $k$, Spiral uniform in $k$, Lines non-uniform in $D$, Lines uniform in $D$, but not in $n$, Lines uniform in $n$ and $D$, and Harmonic Search).
 
@@
 \[ E[T] = c_1 + c_2 / k \]
-Where we are keeping $D = 40$.
+where we are keeping $D = 40$.
 So we are looking to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm.
-Figure~\ref{nonuniformresultsone} and Figure~\ref{nonuniformresultstwo} shows the $k$ being graphed against $k * E[T]$, which we expect to be linear with solve $c_1$ and intercept $c_2$.
+Figure 2 and Figure 3 shows $k$ being graphed against $k * E[T]$, which we expect to be linear with slope $c_1$ and intercept $c_2$.
 Using linear regression, we are able to estimate the values of $c_1$ and $c_2$.
@@
 \[ E[T] = f(\log k)(c_1 + c_2 / k) \]
-Where we set $f(x) = x^2 + 1$. This satisfies all our constraints from the theorems in the paper.
+where we set $f(x) = x^2 + 1$. This satisfies all our constraints from the theorems in the paper.
 Again, we keep $D = 40$ and we want to compute the constants $c_1$ and $c_2$ for the Spiral and Lines algorithm.
-Figure~\ref{uniformresultsone} and Figure~\ref{uniformresultstwo} shows the $k$ being graphed against $k * E[T]/f(\log k)$, which we expect to be linear with solve $c_1$ and intercept $c_2$.
+Figure 4 and Figure 5 shows $k$ being graphed against $k * E[T]/f(\log k)$, which we expect to be linear with slope $c_1$ and intercept $c_2$.
 Using linear regression, we are able to estimate the values of $c_1$ and $c_2$.
@@
 \subsubsection{Interpretation}
-This shows that in fact, when only analyzing runtime.
-The Spiral algorithm performs better than the Lines algorithm in both uniform and non-uniform cases.
-This of course, was expected, since the Lines algorithm optimizes for memory.
+This shows that when we only analyze runtime, the Spiral algorithm performs better than the Lines algorithm in both uniform and non-uniform cases.
+This was expected since the Lines algorithm optimizes for memory.
 
-Some interesting thing we noted is that when running the Lines algorithm in the non-uniform flavour in $D$, we noted that there were lower order terms which were important in the runtime.
-Figure~\ref{nonuniforminD} and Figure~\ref{nonuniforminDtwo} show how there are lower order terms that are hidden in the asymptotics that do make a difference in the experiments for small $k$.
-In fact, the assumption that $E[T] = c_1 + c_2 / k$ gives us the graph Figure~\ref{nonuniforminD} being a line, whereas the assumption $E[t] = c_1/ k + c_2 / k^2$ gives us the graph Figure~\ref{nonuniforminDtwo} being a line, which is much more accurate.
+Some interesting things we noted were that when running the Lines algorithm in the non-uniform in $D$ variant, there were lower order terms which were important in the runtime.
+Figure 6 and Figure 7 show how there are lower order terms that are hidden in the asymptotics that do make a difference in the experiments for small $k$.
+In fact, the assumption that $E[T] = c_1 + c_2 / k$ gives us the graph Figure 6 which is hard to fit with a line, whereas the assumption $E[t] = c_1/ k + c_2 / k^2$ gives us the graph Figure 7 which fits to a line.
+
+Note that we considered the case where $k \leq 200$, and it turns out that real ant colonies can be this small.
+The acorn ant is known to have colonies of around 100 worker ants, and since the goal of the lines algorithm is to be slightly more realistic than the other algorithms, this analysis shows that perhaps lower order terms in $k$ should not be neglected.
 

### 2014-12-09 paper/draft.tex
finished revising section 2

@@
 There is a simple $\Omega(D+D^2/k)$ lower bound which follows from the following argument.
+
 The time it takes $T$ for an algorithm to run must satisfy $T \geq D$, or else it is not even possible to reach treasure $D$ units away.
-
 Also, $T$ must satisfy $T \geq D^2/4k$.
@@
 
-Note this lower bound holds even if the agents knows the total number of agents.
+Note this lower bound holds even if the agents know the total number of agents.
 
@@
 
-And each algorithm has two flavours: \emph{uniform} and \emph{non-uniform}.
+Each algorithm has two flavors: \emph{uniform} and \emph{non-uniform}.
 We say that an algorithm is non-uniform in parameter $p$ if $p$ is an input to the algorithm.
@@
 The spiral and Harmonic search algorithms are similar strategies and were introduced by \cite{feinerman2012collaborative}.
-Both rely on the ``spiral" procedure, in which an agent covers a space of $\sqrt{d}$ grid cells in $O(d)$ time.
+Both rely on the ``spiral" procedure, in which an agent covers a $\sqrt{d} \times \sqrt{d}$ region of grid cells in $O(d)$ time.
 Figure~\ref{fig:spiral} shows a possible spiral routine.
-There will be two kinds of spiral algorithms, non-uniform in $k$ and uniform in $k$.
+There will be two kinds of spiral algorithms: non-uniform in $k$ and uniform in $k$.
 There will be three kinds of lines algorithms, non-uniform in $D$, non-uniform in $k$, and uniform in both $k$ and $D$.
-The Harmonic search algorithm is extremely simple and uniform in both $k$ and $D$.
+The Harmonic search algorithm is extremely simple and is uniform in both $k$ and $D$.
 

### 2014-12-09 paper/draft.tex
revised sections 3-5

--- 2014-12-09 paper/draft.tex
@@
 Given the number of agents taking part in the search, we could imagine an algorithm in which the grid in divided into $k$ parts, similar to a pizza being divided into $k$ equal parts.
-Each agent could cover his portion, and this would yield an asymptotically optimal algorithm.
+Each agent could cover its portion, and this would yield an asymptotically optimal algorithm.
 However, this assumes that the agents can communicate with each other and decide which portion belongs to which agent.
@@
 
-This is what the spiral algorithms does when its non-uniform in $k$.
+This is what the spiral algorithms does when it's non-uniform in $k$.
 
@@
 Once we have the spiral algorithm non-uniform in $k$, we can make it uniform in $k$ by successively doubling estimates of $k$.
-This means that at each stage, we take a guess of what $k$ is, and we simulate the algorithm.
+This means that at each stage, we take a guess of what $k$ is, and we simulate the algorithm given the guess.
 There is some additional bookkeeping to ensure that enough iterations are made, but the optimization is similar.
@@
 
-The lines algorithm is the study of \cite{lenzen2014trade}, where they cover a lines algorithm which is non-uniform in $D$ and non-uniform in $k$.
+The lines algorithm is the study of \cite{lenzen2014trade}, where they cover a lines algorithm that is non-uniform in $D$ and one that is uniform in $D$ but non-uniform in $k$.
 We use the ideas of \cite{feinerman2012collaborative} to design a lines algorithm which is uniform in both $k$ and $D$.
 The lines algorithm has many optimizations since \cite{lenzen2014trade} are trying to reduce \emph{selection complexity}.
-Selection complexity is a metric which measures how likely an algorithm is to occur naturally in nature.
+Selection complexity is a metric which measures how likely an algorithm is to occur in nature.
 Of course, this notion is very vague, but formally, the selection complexity $\chi$ of an algorithm $A$ is $\chi(A) = b + \log l$ where $b$ is the amount of memory usage and $l$ is smallest $l$ for which the algorithm does not need finer probabilities than $2^{-l}$.
 In \cite{lenzen2014trade}, Lenzen et al.
-provided a lines algorithm with selection complexity $O(\log \log D)$.
+provided a lines algorithm with selection complexity $O(\log \log D)$, as opposed to $O(\log D)$ for the spiral algorithms and $\infty$ for harmonic search.
 
@@
 \Procname{Each agent performs the following iteration}
-\li dir[0] $\leftarrow$ up, dir[1] $\leftarrow$ down
-\li $i \leftarrow C_{\frac{1}{2}}$
-\li moveDirection($i$)
+\li \If $C_{\frac{1}{2}} = 0$ \Then
+\li moveDirection(up)
+\li \Else moveDirection(down) \End
 \li \If $C_{\frac{1}{2}} = 0$ \Then
@@
 This would require $\log D$ memory, which we cannot afford; however, it is an assumption in the model that agents can return to the origin.
-
-% TO DO
-The sketch of the proof of correctness is the following ...????
 
@@
 
-The main idea for achieving uniformity in $k$ is borrowed from \cite{feinerman2012collaborative}: we start with a small guess for $k$, run the algorithm uniform in $D$ under this assumption, and then double out guess for $k$ and repeat.
-The implementation actually interleaves the increments of the $D$ and $k$ estimates, running a certain number of iterations of the non-uniform subroutine for each estimate.
+The main idea for achieving uniformity in $k$ is borrowed from \cite{feinerman2012collaborative}: we start with a small guess for $k$, run the algorithm uniform in $D$ under this assumption, and then double our guess for $k$ and repeat.
+The implementation actually interleaves the increments of the $D$ and $k$ estimates, probabilistically running a number of iterations of the non-uniform subroutine for each estimate based on the outcomes of a series of coin flips, as explained in the subsection above.
+
+The expected time complexity of this algorithm is the same as that for the uniform variant of the spirals algorithms.
 
